Untitled

### 2020-11-13 Rmd/Ideas_and_meetings/Ideas.Rmd
data org

Plant pollinator intaractions are a keystone process for ecosystem functioning. However, we lack comprehensive information from both plants and pollinators that can inform from this mutualistic interaction worldwide. In order to tackle this, we have selected 30 networks distributed across the world and looked for key floral traits of plant-pollinator interactions for a total of 1600 species. Here we look how these floral traits shape the different plant-pollinator networks and the main fuctional groups of insect pollinating species. Giving the different nature of the data collated we do not compare across networks and we focus on the main general patterns/results within network. We have conducted our analysis at 3 levels, 1) unique networks, 2) metawebs and by 3) grouping both. We find that specific traits are associated with different guilds of floral visitors within these networks. 
We also highlight the lack of information about traits and the reproductive biology of the plant species of these networks. Our work shows the importance of deepen in species traits in order to understand key processes that can be seen with network metrics and highlights the importance of elemental ecology for species conservation.

@@

>>>>

Plant pollinator intaractions are a keystone process for ecosystem functioning. However, we lack comprehensive information from both plants and pollinators that can inform from this mutualistic interaction worldwide. [frase que no significa nada, information on what? to inform what?]() In order to tackle this, we have selected 30 networks distributed across the world and looked for key floral traits of plant-pollinator interactions for a total of 1600 species. Here we look how these floral traits shape the different plant-pollinator networks and the main fuctional groups of insect pollinating species. Giving the different nature of the data collated we do not compare across networks and we focus on the main general patterns/results within network. We have conducted our analysis at 3 levels, 1) unique networks, 2) metawebs and by 3) grouping both. We find that specific traits are associated with different guilds of floral visitors within these networks. 
We also highlight the lack of information about traits and the reproductive biology of the plant species of these networks. Our work shows the importance to deepen in species traits in order to understand key processes that structure network metrics and highlights the importance of basic ecology for species conservation.
[buen abstract!]()

@@

[ideal añadir nectar production]()

### 2020-11-13 Rmd/Trait_by_World_map/World_Map_Compatibility_Systems.Rmd
data org

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=10,fig.width=40,fig.align = 'center'}
#WORLDPLOT WITH BREEDING SYSTEMS

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
library(effsize)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(cowplot)
library(gridExtra)
library(egg)
library(magrittr)
library(multipanelfigure)
library(grid)
# READ LONG FORMAT DATA
setwd("~/R_Projects/Reproductive Traits")
Long_format_metawebs <- readRDS("Data/RData/Long_format_metawebs.RData")

#READ TRAIT DATA IN ORDER TO MERGE
data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
data <- data[,c(1,4,6,7,8,15,27)]
levels(as.factor(data$Breeding_system))
#Filter data for columns of interest
data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
#Rename column to merge
colnames(data_filtered)[1] <- "Plant_species"
#Convert to factor 
data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)

#Group breeding system per metaweb or web
all_summary_breeding_system <- dcast(all_species_per_network,Id~Breeding_system,value.var = "Breeding_system")

#Cleaning NA and one unfinished network
all_summary_breeding_system <- all_summary_breeding_system[-c(6,30),]

#Removing ".csv" from the Id to megere with coordinates
all_summary_breeding_system$Id <- gsub("\\..*","",all_summary_breeding_system$Id)

#Merge coordinates and data 
data_merged <- merge(metadata_sub, all_summary_breeding_system)

data_merged[,c(3,4,6:19)] <- sapply(data_merged[,c(3,4,6:19)],as.numeric)
sapply(data_merged, class)
data_merged$Id <- as.factor(data_merged$Id)
str(data_merged)
#Prepare data for plotting
data_merged$Hermaphroditism <- data_merged$hermaphrodite
data_merged$Dioecy <- data_merged$androdioecious + data_merged$androgynodioecious + data_merged$dioecious+
  data_merged$gynodioecious + data_merged$monoecious_dioecious + data_merged$`polygamo-dioecious`+
  data_merged$subdioecious

data_merged$Monoecy <- data_merged$andromonoecious + data_merged$gynomonoecious + data_merged$monoecious
+ data_merged$submonoecious

data_merged_sub <- data_merged[, c(1:6, 20:22)]
#Plot data
world <- map_data('world')

p1 <- ggplot(world, aes(long, lat)) +
  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE) +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
 labels = c("Hermaphroditism", "Dioecy", "Monoecy"),values = c("Hermaphroditism" = "#4DAF4A",
 "Monoecy" = "#984EA3","Dioecy" = "orange")) +labs(title = "Breeding system",subtitle = "",
  caption = "",fill = NULL) + theme(legend.position = c(0.15, 0.010),legend.justification = c(1, 0),legend.text=element_text(size=5),legend.key.size = unit(0.16, "cm")) +

@@

p2 <- ggplot(world, aes(long, lat)) +

@@

  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE) +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 

@@

#Load Libraries
library(readxl)
library(ggplot2)
library(dbplyr)
library(scatterpie)
library(reshape2)
# READ LONG FORMAT DATA
setwd("~/R_Projects/Reproductive Traits")

#READ TRAIT DATA IN ORDER TO MERGE
data <- read.csv("Data/Data_processing/all.csv", stringsAsFactors = F)
data <- data[,c(1,4,6,7,8,51,27)]
levels(as.factor(data$Breeding_system))
#Filter data for columns of interest
data_filtered <- subset(data, Info_level=="flower"|Info_level=="capitulum"|Info_level=="inflorescence"|Info_level=="NA")
#Rename column to merge
colnames(data_filtered)[1] <- "Plant_species"
#Convert to factor 
data_filtered <- as.data.frame(data_filtered, stringsAsFactors = TRUE)

#Group breeding system per metaweb or web
all_summary_life_form <- dcast(all_species_per_network,Id~life_form,value.var = "life_form")
#Cleaning NA and one unfinished network
all_summary_life_form <- all_summary_life_form[-c(6,30),-c(6)]
#Removing ".csv" from the Id to megere with coordinates
all_summary_life_form$Id <- gsub("\\..*","",all_summary_life_form$Id)

#Merge coordinates and data 
data_merged <- merge(metadata_sub, all_summary_life_form)

data_merged_sub_ord[,c(3,4,7:10)] <- sapply(data_merged_sub_ord[,c(3,4,7:10)],as.numeric)
str(data_merged_sub_ord)

p3 <- ggplot(world, aes(long, lat)) +
  geom_map(map=world, aes(map_id=region), fill="white", color="grey") +
  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE) +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 
                     data = data_merged_sub_ord, cols = colnames(data_merged_sub_ord[,c(7:10)]),alpha=.8)+ 
  scale_fill_manual(breaks = colnames(data_merged_sub_ord[,c(7:10)]),
                    labels = c("Herb", "Shrub", "Tree", "Vine"),values = c("herb" = "#4DAF4A",
                                                                           "shrub" = "#984EA3","tree" = "orange", "vine" = "lightblue")) +labs(title = "Life form",subtitle = "",
                                                                                                                                               caption = "",fill = NULL) + theme(legend.position = c(0.12, 0.009),legend.justification = c(1, 0),
                                                                                                                                                                                 axis.ticks = element_blank(),legend.key.size = unit(0.2, "cm")) +

grid.arrange(p1, p2, p3, nrow=3)

 #grid.draw(arrangeGrob(ggplotGrob(p1),ggplotGrob(p2),nrow=2))
#mylegend
 dev.off()

>>>>

---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE}

@@

p <- ggplot(world, aes(long, lat)) +

@@

  coord_quickmap()+ylab("Latitude")+ xlab("Longitude")+coord_equal() + coord_sf( ylim = c(-60, 100), expand = FALSE)
p +  geom_scatterpie(aes(x=longitude, y=latitude,group=Id), 

@@
